### 2020-10-10 paper/sections/design.tex
the second revision

%		\STATE \textbf{2) Reward calcuation.} 
		\STATE \textbf{2) Reward calcuation} 
		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
		{\color{revise2} \STATE compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design}

>>>>

%		\STATE \textbf{2) Reward calcuation.} 
		\STATE \textbf{2) Reward calcuation} 
		\STATE Compress image $ x_t $ at quality $ c_t $ to upload
		\STATE Receive $ (\vec{y}_{\rm ref}, \vec{y}_c) $ from the cloud service
		{\color{revise2} \STATE Compute reward $ r \leftarrow R(\Delta s, \mathcal{A}_c) $ according to \ref{subsec: reward} Reward Feedback Design}
